Model based reinforcement learning at FERMI FEL

### 2020-11-16 main.tex
txs auto checkin

% \begin{algorithm}[ht]
% \caption{On-policy policy gradient with Monte Carlo estimator \label{alg:pg}}
% \begin{algorithmic}[1]
% \State initialise $\theta_0$
% \For{iteration $k \in [0, \dots, K]$}
% \State sample trajectories $\{\traj_i\}$ by running $\policy_{\theta_k}(\ba_t|\bs_t)$ \Comment{each $\traj_i$ consists of $\bs_{i,0},\ba_{i,0},\dots,\bs_{i,H},\ba_{i,H}$}
% \State compute $\return_{i,t} = \sum_{t'=t}^H \discount^{t'-t} \reward(\bs_{i,t},\ba_{i,t})$
% \State fit $b(\bs_t)$ to $\{\return{i,t}\}$ \Comment{use constant $b_t = \frac{1}{N}\sum_i \return{i,t}$, or fit $b(\bs_t)$ to $\{\return{i,t}\}$}
% \State compute $\hat{A}(\bs_{i,t},\ba_{i,t}) = \return_{i,t} - b(\bs_t)$
% \State estimate $\nabla_{\theta_k} J(\policy_{\theta_k}) \approx \sum_{i,t} \nabla_{\theta_k} \log \policy_{\theta_k}(\ba_{i,t} | \bs_{i,t}) \hat{A}(\bs_{i,t},\ba_{i,t})$
% \State update parameters: $\theta_{k+1} \leftarrow \theta_k + \alpha \nabla_{\theta_k} J(\policy_{\theta_k})$
% \EndFor
% \end{algorithmic}
% \end{algorithm}

@@

\appendix
\section{A non-linear standard control problem}
To provide some transparency of these studies we provide results on a famous classical standard control problem, the inverted pendulum. It is a non-linear low dimensional continuous control problem. 
\section{NAF2 details}\label{appendix:pernaf}

>>>>

\begin{algorithm}[ht]
\caption{On-policy policy gradient with Monte Carlo estimator \label{alg:pg}}
\begin{algorithmic}[1]
\State initialise $\theta_0$
\For{iteration $k \in [0, \dots, K]$}
\State sample trajectories $\{\traj_i\}$ by running $\policy_{\theta_k}(\ba_t|\bs_t)$ \Comment{each $\traj_i$ consists of $\bs_{i,0},\ba_{i,0},\dots,\bs_{i,H},\ba_{i,H}$}
\State compute $\return_{i,t} = \sum_{t'=t}^H \discount^{t'-t} \reward(\bs_{i,t},\ba_{i,t})$
\State fit $b(\bs_t)$ to $\{\return{i,t}\}$ \Comment{use constant $b_t = \frac{1}{N}\sum_i \return{i,t}$, or fit $b(\bs_t)$ to $\{\return{i,t}\}$}
\State compute $\hat{A}(\bs_{i,t},\ba_{i,t}) = \return_{i,t} - b(\bs_t)$
\State estimate $\nabla_{\theta_k} J(\policy_{\theta_k}) \approx \sum_{i,t} \nabla_{\theta_k} \log \policy_{\theta_k}(\ba_{i,t} | \bs_{i,t}) \hat{A}(\bs_{i,t},\ba_{i,t})$
\State update parameters: $\theta_{k+1} \leftarrow \theta_k + \alpha \nabla_{\theta_k} J(\policy_{\theta_k})$
\EndFor
\end{algorithmic}
\end{algorithm}

@@

\appendix
\section{A non-linear standard control problem}
To provide some transparency of these studies we provide results on a famous classical standard control problem, the inverted pendulum. It is a non-linear low dimensional unsolved continuous control problem, which means there is no threshold for the reward to terminate an episode. The episode length is set to 200 steps.
\section{NAF2 details}\label{appendix:pernaf}
